### 2012-03-20 doc/theses/mikula/proposed_algorithm.tex
Master thesis: In progress.

Some pseudo code algorithms in the following sections need to determine a class of a node. The node's direct class can be determined by function $c$ from the definition of the syntax tree in Definition \ref{DEF_syntax_tree}, and hence, we also can determine its indirect classes. For the purpose of pseudo code, we define the following function.

@@

>>>>

Some pseudo-code algorithms in the following sections need to determine a class of a node. The node's direct class can be determined by function $c$ from the definition of the syntax tree in Definition \ref{DEF_syntax_tree}, and hence, we also can determine its indirect classes. For the purpose of pseudo code, we define the following function.

@@

\subsection{Syntax Tree Example}

\begin{lstlisting}[float, caption=Sample query 1., frame=single, label=listing_sample_query_1]
declare namespace local = "http://www.foobar.org";
declare function local:convert($v as xs:decimal?)
  as xs:decimal?
{
  2.20371 * $v (: convert Dfl to Euro :)
};

for $i in /site/open_auctions/open_auction
return local:convert(zero-or-one($i/reserve))
\end{lstlisting}

\begin{figure}
\label{FIG_syntax_tree_1}
\caption{Sample syntax tree 1.}
\includegraphics[scale=0.6]{syntax_tree_1.eps}
\end{figure}

A syntax tree constructed from sample query in Listing \ref{listing_sample_query_1} is shown in Figure \ref{FIG_syntax_tree_1}.
